## Macroecology - testing the species-abundance distribution

```{r, warning=FALSE, message=FALSE}
library(rbison)
library(ggplot2)
library(plyr)
library(doMC)
```

Define a vector of species names

```{r, warning=FALSE, message=FALSE}
mynames <- c("Helianthus annuus", "Pinus contorta", "Poa annua", 
  "Madia sativa", "Arctostaphylos glauca", "Heteromeles arbutifolia",
  "Symphoricarpos albus", "Ribes viburnifolium", "Diplacus aurantiacus", 
  "Salvia leucophylla", "Encelia californica", "Ribes indecorum", 
  "Ribes malvaceum", "Cercocarpus betuloides", "Penstemon spectabilis")
```

Define a function to get data needed, here just the summary data, then pull out just the _total_ column and make a `data.frame` along with the input taxon name

```{r}
getdata <- function(x) {
  tmp <- bison(species = x, what='summary')$summary
  data.frame(x, abd=tmp$total)
}
```

Get the data by passing each name to the `getdata` function

```{r, warning=FALSE, message=FALSE}
out <- ldply(mynames, getdata)
```

Plot species-abundance distribution using the `radfit` function in vegan

```{r, warning=FALSE, message=FALSE}
library(vegan)
plot(radfit(out$abd))
```