## Finding countries species are found in using rgbif

### Load some libraries

```{r}
library(rgbif)
library(plyr)
library(doMC)
```

### List of bird species

```{r}
spplist <- c('Geothlypis trichas','Tiaris olivacea','Pterodroma axillaris','Calidris ferruginea','Pterodroma macroptera','Gallirallus australis','Falco cenchroides','Telespiza cantans','Oreomystis bairdi','Cistothorus palustris')
```

### Get GBIF keys for each taxon

```{r, cache=TRUE}
keys <- sapply(spplist, function(x) name_backbone(x, rank="species")$usageKey)
# remove NULLs
keys <- compact(keys)
```

### Get country names (from rgbif package)

For brevity we'll just use 25 countries

```{r, cache=TRUE}
countrynames <- as.character(isocodes$gbif_name)[1:25]
```

### Get data

Function to get data for each name

```{r, cache=TRUE}
occ_by_countries <- function(spkey){
  occ_count_safe <- plyr::failwith(NULL, occ_count)
  tmp <- lapply(countrynames, function(x) occ_count_safe(spkey, country=x))
  names(tmp) <- countrynames
  tmp[grep("No enum", tmp)] <- NA
  tmp
}
```

Get data for each species

```{r, cache=TRUE}
registerDoMC(cores=4) 
out <- llply(keys, occ_by_countries, .parallel=TRUE)
```

Or you could do the same without doing in parallel, but will be slower of course

```{r eval=FALSE}
out <- lapply(keys, occ_by_countries)
```

### Assign species name to each output element

Then make a data.frame, then remove NA rows

```{r, cache=TRUE}
names(out) <- spplist
df <- ldply(out, function(x){
  tmp <- ldply(x)
  names(tmp)[1] <- "country"
  tmp
})
df <- na.omit(df) # remove NAs (which were caused by errors in country names)
```

And you can get only countries they're found in by removing zeros

```{r, cache=TRUE}
# Get only countries found in
df_foundin <- df[!df$V1==0,]
```

Look at first and last six rows

```{r, cache=TRUE}
head(df_foundin); tail(df_foundin)
```