### spocc - Make some maps!

### Load libraries

```{r load, message=FALSE, warning=FALSE}
library(spocc)
library(rCharts)
```

### spocc unifies access to biodiversity data across sources

```{r sources, message=FALSE, warning=FALSE}
out <- occ(query='Accipiter striatus', from='gbif')
out # prints summary of output data
out$gbif # GBIF data w/ metadata
out$ebird$data # empty
out$gbif$meta #  metadata, your query parameters, time the call executed, etc. 
out$gbif$data # just data
```

And you can squash together data from sources easily

```{r manysources, message=FALSE, warning=FALSE}
out <- occ(query='Accipiter striatus', from=c('gbif','bison'))
df <- occ2df(out)
head( df ); tail( df )
```


### Make a map using Shiny locally (uses rCharts)

**This won't work using RStudio server in the browser**

Try changing the species names to whatever you like and press **Submit**

Or change the background map, or the color palette. 

```{r shinymap, eval=FALSE}
mapshiny()
```


### Make a map using Leaflet.js, a javascript mapping library

```{r leaflet, eval=FALSE}
dat <- occ(query='Danaus plexippus', from='gbif', gbifopts=list(georeferenced=TRUE))
dat <- occ2df(dat)
mapleaflet(data=dat)
```


### Make a map using GitHub gists

If you have a Github Account, you can get an interactive map on Github in one line of code. The map will open in your default browser. 

```{r gistmap, eval=FALSE}
spp <- c('Danaus plexippus','Accipiter striatus','Pinus contorta')
dat <- occ(query=spp, from='gbif', gbifopts=list(georeferenced=TRUE))
dat <- fixnames(dat)
dat <- occ2df(dat)
mapgist(data=dat, color=c("#976AAE","#6B944D","#BD5945"))
```