Creating maps with SPOCC
========================================================

*What is geoJSON?*

A way to encode geographic information as a JSON object, and render it on the web.
---

*A simple example with species occurrence data*

First let's grab some data

```{r grab some data}
library(spocc)

red_tailed_hawk <- occ(query = "Buteo jamaicensis", from = c("gbif","ebird"),limit=35, ebirdopts = list(region='US'))

rt_hawk <-  occ2df(red_tailed_hawk)

```


Now we can create some maps.

```{r leaflet}
#### Map with leaflet.js
mapleaflet(rt_hawk)

## put the map up as a gist
mapgist(data = rt_hawk)

```


Let's try this with multiple species

```{r multiple species}
 spp <- c('Accipiter gentilis','Accipiter striatus','Accipiter cooperii')
dat <- occ(query = spp, from = "gbif", gbifopts = list(georeferenced = TRUE))
dat <- fixnames(dat)
dat <- occ2df(dat)
mapgist(data = dat, color = c("#976AAE", "#6B944D", "#BD5945"))


```

If you want to render it full screen, you just append `https://render.github.com/view/geojson?url=` to your source, so the previous map can become: `https://render.github.com/view/geojson?url=https://gist.githubusercontent.com/emhart/9191388/raw/341475808fbadf26cf4eeb2b237f9bd9cae39e4d/gistmap.geojson`

*Exercise*

Choose a species of interest, or multiple, and make a map with leaflet or mapgist.
